Flowchart of Current Algorithm

### 2008-10-13 docs/flowchart/paper.tex
some minor typos
in some places where we need separate spherical details, I'm going to refer to "paper IV" and use that as our working notes so we don't have to keep two documents updated.  Once we are more "final" in paper IV we can add it in here.

Here we outline the algorithm currently implemented in the code.  Our
starting point for this description are the series of papers describing
the development of the algorithm:
\begin{itemize}
\item {\em Low Mach Number Modeling of Type Ia
  Supernovae. I. Hydrodynamics}, A.~S.~Almgren, J.~B.~Bell, 
  C.~A.~Rendleman, \& M.~Zingale 2006, ApJ, 637, 922 (henceforth
  paper~I)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. II. Energy
  Evolution} A.~S.~Almgren, J.~B.~Bell, C.~A.~Rendleman, \& M.~Zingale
  2006, ApJ, 649, 927 (henceforth paper~II)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. III. Reactions}
A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, \& M.~Zingale
  2008, ApJ, 684, 449 (henceforth paper~III)
\end{itemize}

@@

\item {\bf Correct Base}
$[\rho_0^{\inp}, (\nabla\cdot\etarho)^{\inp}] \rightarrow (\rho_0^{\outp})$
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$.  For both plane-parallel and spherical
we use
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \dt (\nabla\cdot\etarho)^{\inp}_j \enskip . 
\end{equation}

@@

\MarginPar{need to add spherical}

@@

\item Define an edge-centered $\etarho^{\nph,\star}$, cell-centered 
$(\nabla\cdot\etarho)^{\nph,\star}$, and cell-centered $\psi_j^{\nph,\star}$:

@@

\begin{eqnarray}
 \etarho^{\nph,\star}   &=&  {\rm {\bf Avg}} \left( (\uadvone \cdotb \er + w_0^{\nph,\star}) 
\rho^{(1),\nph,\star} \right) - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} 
 \enskip , \nonumber \\ \\
(\nabla\cdot\etarho)_j^{\nph,\star} &=& 
\frac{\eta_{\rho,j+\myhalf}^{\nph,\star}-\eta_{\rho,j-\myhalf}^{\nph,\star}}{\Delta r} \enskip , \\
 \psi_j^{\nph,\star}  &=&  \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph,\star} + \eta_{\rho,j+\myhalf}^{\nph,\star}\right) g \enskip .
\end{eqnarray}

@@

\item {\bf Correct Base}
$[\rho_0^{(2),\star}, (\nabla\cdot\etarho)^{\nph,*}] \rightarrow (\rho_0^{n+1,\star})$.

@@

\item Diffuse the enthalpy through a time interval of $\dt$.  Compute $\kth^{(1)}, c_p^{(1)}$, and $\xi_k^{(1)}$ from $\rho^{(1)}, T^{(1)}$, and $X_k^{(1)}$ as inputs to the equation of state.  The update is given by:
\begin{eqnarray}
(\rho h)^{(2),\star} &=& (\rho h)^{(2'),\star} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(2),\star} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(2),\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2),\star}$,
\begin{eqnarray}
\left(\rho^{(2),\star} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla\right)h^{(2),\star} &=& (\rho h)^{(2'),\star} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(2),\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
\item Update the temperature
\begin{equation}
T^{(2),\star} = T\left(\rho^{(2),\star}, h^{(2),\star}, X_k^{(2),\star}\right) {\hbox{ \rm using the equation of state.}}
\end{equation}

@@

\begin{enumerate}
\renewcommand{\theenumi}{{\bf \alph{enumi}}}
\item Define:
\begin{equation}
  S^{n+1,\star} =  -\sigma  \sum_k  \xi_k  (\omegadot_k)^{(2),\star}  + 
  \sigma \Hnuc^{(2),\star} +
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  ({\omegadot}_k)^{(2),\star}  
  + \sigma \Hext \enskip .
\end{equation} 
where $(\omegadot_k)^{(2),\star} = (\rho \omegadot_k)^{(2),\star} / \rho^{(2),\star}$
and the remaining quantities are defined using $X_k^{n+1,\star},$ $\rho^{n+1,\star},$ 
and $T^{n+1,\star}$ from step 5.
Then define
\begin{equation}
 S^\nph = \frac{S^n + S^{n+1,\star}}{2} \enskip. 
\end{equation}

\item Define:
\begin{equation}
\overline{S}^{\nph} = {\mathrm{\bf Avg}} (S^{\nph}) \enskip.
\end{equation}

@@

%--------------------------------------------------------------------------
% STEP 7
%--------------------------------------------------------------------------
\item[Step 7.] {\em Construct the final edge-based advective velocity}, $\uadvtwo$:

The procedure to construct $\uadvtwo$ is described in detail in Appendix B of paper III
and is analogous to the procedure used in step 2, but with updated values
for $w_0$ and $\pizero.$  We note that $\uadvtwo$ satisfies the discrete versions of 
equations (\ref{eq:udoterzero}) and (\ref{eq:tildeconstraint}).   The discretization
with the volume discrepancy correction is:
\begin{eqnarray}
\nablab \cdotb \left(\beta_0^{\nph,\star} \uadvtwo\right) &=& 
\beta_0^{\nph,\star} \left(S^{\nph} - \overline{S}^{\nph}\right) \nonumber \\
&& + \frac{f}{\gammabar^{\nph,\star} p_0^{\nph,\star}}
\left(\frac{p(\rho,h,X_k)^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right)
\enskip , \nonumber \\
\end{eqnarray}
\begin{equation}
\beta_0^{\nph,\star} = \frac{ \beta_0^n +  \beta_0^{n+1,\star} }{2} \enskip .
\end{equation}

@@

\item Define an edge-centered $\etarho^{\nph}$, cell-centered 
$(\nabla\cdot\etarho)^{\nph}$, and a cell-centered $\psi_j^{\nph}$,

@@

\begin{eqnarray}
 \etarho^{\nph}   &=&  {\rm {\bf Avg}} \left( (\uadvtwo \cdotb \er + w_0^{\nph}) 
\rho^{(1),\nph} \right) - w_0^{\nph} \rho_0^{\nph,{\rm pred}} \enskip , \nonumber \\ \\
(\nabla\cdot\etarho)_j^{\nph} &=& 
\frac{\eta_{\rho,j+\myhalf}^{\nph} - \eta_{\rho,j-\myhalf}^{\nph}}{\Delta r} \enskip , \\
 \psi_j^{\nph}  &=&  \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph} + \eta_{\rho,j+\myhalf}^{\nph}\right) g \enskip .
\end{eqnarray}

@@

\item {\bf Correct Base}
$[\rho_0^{(2)}, (\nabla\cdot\etarho)^{\nph}] \rightarrow (\rho_0^{n+1})$

%--------------------------------------------------------------------------
% STEP 8.1
%--------------------------------------------------------------------------
\item Diffuse the enthalpy through a time interval of $\dt$.  Compute $\kth^{(2),\star}, c_p^{(2),\star}$, and $\xi_k^{(2),\star}$, from $\rho^{(2),\star}, T^{(2),\star}$, and $X_k^{(2),\star}$ as inputs to the equation of state.  The update is given by:
\begin{eqnarray}
(\rho h)^{(2)} &=& (\rho h)^{(2')} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(2),\star}}{c_p^{(2),\star}}\nabla h^{(2)} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla X_k^{(2)} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla p_0^{(2)} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2)}$,
\begin{eqnarray}
\left(\rho^{(2)} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(2),\star}}{c_p^{(2),\star}}\nabla\right)h^{(2)} &=& (\rho h)^{(2')} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla X_k^{(2)} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla p_0^{(2)} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
\item Update the temperature
\begin{equation}
T^{(2)} = T\left(\rho^{(2)}, h^{(2)}, X_k^{(2)}\right) {\hbox{ \rm using the equation of state.}}
\end{equation}

@@

\begin{enumerate}
\renewcommand{\theenumi}{{\bf \alph{enumi}}}
\item Define:
\begin{equation}
  S^{n+1} =  -\sigma  \sum_k  \xi_k (\omegadot_k)^{(2)}  + \sigma \Hnuc^{(2)} +
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  ({\omegadot}_k)^{(2)}  
   + \sigma \Hext \enskip ,
\end{equation}
where $(\omegadot_k)^{(2)} = (\rho \omegadot_k)^{(2)} / \rho^{(2)}$
and the remaining quantities are defined using $X_k^{n+1},$ $\rho^{n+1},$
and $T^{n+1}$ from step 9.

@@

We determine the new time velocity field from
\begin{equation}
\ut^{n+1} = {\bf V} - \frac{1}{\rho^\nph} \mathbf{G} \phi \enskip ,
\end{equation}
and the new time-centered perturbational pressure from:
\begin{equation}
  \pi^\nph = \frac{1}{\dt} \phi \enskip .
\end{equation}

>>>>

Here we outline the algorithm currently implemented in the code.  Our
starting point for this description are the series of papers describing
the development of the algorithm:
\begin{itemize}
\item {\em Low Mach Number Modeling of Type Ia
  Supernovae. I. Hydrodynamics}, A.~S.~Almgren, J.~B.~Bell, 
  C.~A.~Rendleman, \& M.~Zingale 2006, ApJ, 637, 922 (henceforth
  paper~I)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. II. Energy
  Evolution} A.~S.~Almgren, J.~B.~Bell, C.~A.~Rendleman, \& M.~Zingale
  2006, ApJ, 649, 927 (henceforth paper~II)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. III. Reactions}
A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, \& M.~Zingale
  2008, ApJ, 684, 449 (henceforth paper~III)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. IV. White Dwarf Convection}
A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, \& M.~Zingale,
  in perparation (henceforth paper~IV)
\end{itemize}

@@

\item {\bf Correct Base}
$[\rho_0^{\inp}, (\nabla\cdot\etarho\er)^{\inp}] \rightarrow (\rho_0^{\outp})$
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$.  For both plane-parallel and spherical
we use
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \dt (\nabla\cdot\etarho\er)^{\inp}_j \enskip . 
\end{equation}

@@

See Paper IV for working notes until we finalize this.

@@

\item Define an edge-centered $\etarho^{\nph,\star}$, cell-centered 
$(\nabla\cdot\etarho\er)^{\nph,\star}$, and cell-centered $\psi_j^{\nph,\star}$:

@@

\begin{eqnarray}
 \etarho^{\nph,\star}   &=&  {\rm {\bf Avg}} \left( (\uadvone \cdotb \er + w_0^{\nph,\star}) 
\rho^{(1),\nph,\star} \right) - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} 
 \enskip , \nonumber \\ \\
(\nabla\cdot\etarho\er)_j^{\nph,\star} &=& 
\frac{\eta_{\rho,j+\myhalf}^{\nph,\star}-\eta_{\rho,j-\myhalf}^{\nph,\star}}{\Delta r} \enskip , \\
 \psi_j^{\nph,\star}  &=&  \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph,\star} + \eta_{\rho,j+\myhalf}^{\nph,\star}\right) g \enskip .
\end{eqnarray}

@@

\item {\bf Correct Base}
$[\rho_0^{(2),\star}, (\nabla\cdot\etarho\er)^{\nph,*}] \rightarrow (\rho_0^{n+1,\star})$.

@@

\item Diffuse the enthalpy through a time interval of $\dt$.  Compute $\kth^{(1)}, c_p^{(1)}$, and $\xi_k^{(1)}$ from $\rho^{(1)}, T^{(1)}$, and $X_k^{(1)}$ as inputs to the equation of state.  The update is given by
\begin{eqnarray}
(\rho h)^{(2),\star} &=& (\rho h)^{(2'),\star} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(2),\star} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(2),\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2),\star}$,
\begin{eqnarray}
\left(\rho^{(2),\star} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla\right)h^{(2),\star} &=& (\rho h)^{(2'),\star} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(2),\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
\item Update the temperature
\begin{equation}
T^{(2),\star} = T\left(\rho^{(2),\star}, h^{(2),\star}, X_k^{(2),\star}\right) {\hbox{ \rm using the equation of state.}}
\end{equation}

@@

\begin{enumerate}
\renewcommand{\theenumi}{{\bf \alph{enumi}}}
\item Define
\begin{equation}
  S^{n+1,\star} =  -\sigma  \sum_k  \xi_k  (\omegadot_k)^{(2),\star}  + 
  \sigma \Hnuc^{(2),\star} +
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  ({\omegadot}_k)^{(2),\star}  
  + \sigma \Hext \enskip .
\end{equation} 
where $(\omegadot_k)^{(2),\star} = (\rho \omegadot_k)^{(2),\star} / \rho^{(2),\star}$
and the remaining quantities are defined using $X_k^{n+1,\star},$ $\rho^{n+1,\star},$ 
and $T^{n+1,\star}$ from step 5.
Then define
\begin{equation}
 S^\nph = \frac{S^n + S^{n+1,\star}}{2} \enskip. 
\end{equation}

\item Define
\begin{equation}
\overline{S}^{\nph} = {\mathrm{\bf Avg}} (S^{\nph}) \enskip.
\end{equation}

@@

%--------------------------------------------------------------------------
% STEP 7
%--------------------------------------------------------------------------
\item[Step 7.] {\em Construct the final edge-based advective velocity}, $\uadvtwo$.

The procedure to construct $\uadvtwo$ is described in detail in Appendix B of paper III
and is analogous to the procedure used in step 2, but with updated values
for $w_0$ and $\pizero.$  We note that $\uadvtwo$ satisfies the discrete versions of 
equations (\ref{eq:udoterzero}) and (\ref{eq:tildeconstraint}).   The discretization
with the volume discrepancy correction is
\begin{eqnarray}
\nablab \cdotb \left(\beta_0^{\nph,\star} \uadvtwo\right) &=& 
\beta_0^{\nph,\star} \left(S^{\nph} - \overline{S}^{\nph}\right) \nonumber \\
&& + \frac{f}{\gammabar^{\nph,\star} p_0^{\nph,\star}}
\left(\frac{p(\rho,h,X_k)^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right)
\enskip , \nonumber \\
\end{eqnarray}
\begin{equation}
\beta_0^{\nph,\star} = \frac{ \beta_0^n +  \beta_0^{n+1,\star} }{2} \enskip .
\end{equation}

@@

\item Define an edge-centered $\etarho^{\nph}$, cell-centered 
$(\nabla\cdot\etarho\er)^{\nph}$, and a cell-centered $\psi_j^{\nph}$,

@@

\begin{eqnarray}
 \etarho^{\nph}   &=&  {\rm {\bf Avg}} \left( (\uadvtwo \cdotb \er + w_0^{\nph}) 
\rho^{(1),\nph} \right) - w_0^{\nph} \rho_0^{\nph,{\rm pred}} \enskip , \nonumber \\ \\
(\nabla\cdot\etarho\er)_j^{\nph} &=& 
\frac{\eta_{\rho,j+\myhalf}^{\nph} - \eta_{\rho,j-\myhalf}^{\nph}}{\Delta r} \enskip , \\
 \psi_j^{\nph}  &=&  \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph} + \eta_{\rho,j+\myhalf}^{\nph}\right) g \enskip .
\end{eqnarray}

@@

\item {\bf Correct Base}
$[\rho_0^{(2)}, (\nabla\cdot\etarho\er)^{\nph}] \rightarrow (\rho_0^{n+1})$

%--------------------------------------------------------------------------
% STEP 8.1
%--------------------------------------------------------------------------
\item Diffuse the enthalpy through a time interval of $\dt$.  Compute $\kth^{(2),\star}, c_p^{(2),\star}$, and $\xi_k^{(2),\star}$, from $\rho^{(2),\star}, T^{(2),\star}$, and $X_k^{(2),\star}$ as inputs to the equation of state.  The update is given by
\begin{eqnarray}
(\rho h)^{(2)} &=& (\rho h)^{(2')} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(2),\star}}{c_p^{(2),\star}}\nabla h^{(2)} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla X_k^{(2)} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla p_0^{(2)} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2)}$,
\begin{eqnarray}
\left(\rho^{(2)} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(2),\star}}{c_p^{(2),\star}}\nabla\right)h^{(2)} &=& (\rho h)^{(2')} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla X_k^{(2)} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla p_0^{(2)} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
\item Update the temperature
\begin{equation}
T^{(2)} = T\left(\rho^{(2)}, h^{(2)}, X_k^{(2)}\right) {\hbox{ \rm using the equation of state.}}
\end{equation}

@@

\begin{enumerate}
\renewcommand{\theenumi}{{\bf \alph{enumi}}}
\item Define
\begin{equation}
  S^{n+1} =  -\sigma  \sum_k  \xi_k (\omegadot_k)^{(2)}  + \sigma \Hnuc^{(2)} +
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  ({\omegadot}_k)^{(2)}  
   + \sigma \Hext \enskip ,
\end{equation}
where $(\omegadot_k)^{(2)} = (\rho \omegadot_k)^{(2)} / \rho^{(2)}$
and the remaining quantities are defined using $X_k^{n+1},$ $\rho^{n+1},$
and $T^{n+1}$ from step 9.

@@

We determine the new time velocity field from
\begin{equation}
\ut^{n+1} = {\bf V} - \frac{1}{\rho^\nph} \mathbf{G} \phi \enskip ,
\end{equation}
and the new time-centered perturbational pressure from
\begin{equation}
  \pi^\nph = \frac{1}{\dt} \phi \enskip .
\end{equation}
